---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# riskybiz

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/margarethannum/riskybiz.svg?branch=master)](https://travis-ci.org/margarethannum/riskybiz)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/margarethannum/riskybiz?branch=master&svg=true)](https://ci.appveyor.com/project/margarethannum/riskybiz)
[![Codecov test coverage](https://codecov.io/gh/margarethannum/riskybiz/branch/master/graph/badge.svg)](https://codecov.io/gh/margarethannum/riskybiz?branch=master)
<!-- badges: end -->

The goal of {riskybiz} is to provide both a formula framework for creating competing risks regression objects and also output useful components such as `model.frame` that the original {cmprsk} package does not provide.

# Installation

The {riskybiz} package was written as a wrapper/enhancer to the {cmprsk} package. 

To install the development version of {riskybiz}

```{r eval = FALSE}
install.packages("remotes")
remotes::install_github("margarethannum/riskybiz")
```

# Example


```{r eval=FALSE}

library(gtsummary)
library(cmprsk)

set.seed(123)
trial2 <- trial %>%
mutate(grey = sample(0:2, 200, replace = TRUE, prob = c(0.4, 0.5, 0.1))) %>%
   tidyr::drop_na()

#original crr
covars <- model.matrix(~ age + factor(trt) + factor(grade), trial2)[,-1]
ftime1 <- trial2$ttdeath
fstatus1 <- trial2$grey
mod_orig <- crr(ftime=ftime1,
                fstatus = fstatus,
                cov1 = covars)

# using new wrapper function, accepts data and formula
mod_new <- crr.formula(Surv(ttdeath, grey) ~ age + trt + grade, trial2)

tidy.crr(mod_new)
```


<!-- ## Installation -->

<!-- You can install the development version from [GitHub](https://github.com/) with: -->

<!-- ``` r -->
<!-- # install.packages("devtools") -->
<!-- devtools::install_github("margarethannum/riskybusiness") -->
<!-- ``` -->

